Dear colleague,

After a search for referees, I now have a sufficient number of reports on your submission to International Interactions. I include copies of these excellent reviews at the end of this message.

In aggregate, the reviewers do not make a clear substantive recommendation at this moment. However, in my judgement the paper has the potential to be of considerable interest to many readers. As such, I am offering the opportunity to revise and resubmit it. Please pay careful attention to the reviewers comments. In this case, I believe some rather significant changes will be needed to improve the impact of the manuscript and increase the probability of a successful outcome.

As you will see the reviewers are split on their judgement of the manuscript's merits. My reading was similar to several of the more positive spins on the potential of the work, but agreed with the criticisms that more clarity and translation was needed to broaden the impact of the piece. In particular, the revision should spend more time providing examples of mechanisms and being precise about how this work connects with pre-existing terminology and findings on sanctions (and again being precise about distinctions). Too much of the paper reads like a methodology exercise conducted on convenient data (which can be quite informative, but does not do the work of telling us why it is important). Moreover, some simple revisions that highlight why the specification provided brings inferences closer to theoretical expectation about the data generation process (again, from the pre-existing literature) could go a long way to broadening the impact of the manuscript. The reviewers will be looking for improved clarity in the theoretical concepts and mechanisms in the next draft.

If you accept this opportunity, I will then send the revision again to two of the reviewers for an up-or-down recommendation, based on the clarity of the presentation and its substance. Small further changes would be permitted; the need for large ones would end the process.

Along with your revised manuscript, we would appreciate if you could provide a memo detailing how you respond to the reviewers' suggestions. Use the space provided in step 1 of the revision process to respond. Further, please tell me within the coming days if you are planning to accept this offer and if so, when you would be able to resubmit a revised version.

To revise your manuscript, log into https://mc.manuscriptcentral.com/gini and enter your Author Center, where you will find your manuscript title listed under "Manuscripts with Decisions."  Under "Actions," click on "Create a Revision."  Your manuscript number has been appended to denote a revision.

You will be unable to make your revisions on the originally submitted version of the manuscript.  Instead, revise your manuscript using a word processing program and save it on your computer. Once the revised manuscript is prepared, you can upload it and submit it through your Author Center.
When submitting your revised manuscript, you will be able to respond to the comments made by the reviewers in the space provided.  Please use this space to document any changes you make to the original manuscript.  In order to expedite the processing of the revised manuscript, please be as specific as possible in your response to the reviewers. If you have any questions about directions for revisions, please do not hesitate to contact me.

IMPORTANT:  Your original files are available to you when you upload your revised manuscript.  Please delete any redundant files before completing the submission.

Thank you for your interest in International Interactions.

Sincerely,

Professor Michael Colaresi
co-Editor of International Interactions